Make any stupid plot you want

### 2020-12-07 draft/sections/math.tex
is U_sigma singular

\begin{figure}[ht]
    \label{fig:fiberbundle}
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
\end{figure}

@@

\begin{figure}[ht]
    \includegraphics[width=0.4\linewidth]{figures/sections/math/k_qspace.png}
    \label{fig:kquotient}
\end{figure}

$K$ is the quotient space of $E$, meaning it is the set of equivalence classes of elements $p$ in of $E$ defined via the map $\pi: E \rightarrow K$ that sends each point $p \in E$ to its equivalence class in $[p] \in K$ \cite{QuotientSpaceTopology2020,QuotientSpaceTopology2020}. As shown in figure~\ref{fig:kquotient}, the fibers $F$ divide $E$ into smaller spaces consisisting of $F$ and an open set neighborhood around $F$. This subdivision is projected down to the toplology $\tau_k$

@@

\begin{figure}[ht]
    \label{fig:k_data}
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
    %% add box around neighboring P and Map
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}

We use $K$ to encode the connectivity of the points $p$, such as the ones in figure~\ref{fig:k_data} that only store temperature data. In a timeseries, the temperature $p$ at timme $t$ is dependent on the value at $p_{t-1}$ and $\p_{t+1}$ is dependent on the value in $p_t$; this connectivity is expressed as a one dimensional $K$ where $K$ is the number line. In the case of the map, every point $p$ is dependent on its nearest neighbors on the plane, and one way to express this is by encoding $K$ as a plane. $K$ does not know the time or latitude or longitude of the point - those are metadata variables potentially encoded in $p$ because they are ways of describing the connectivity rather than the connectivity itself. The mapping $sigma: K \rightarrow E$ provides the binding between the key on $K$ and the value $p$ in $E$ \cite{munznerChDataAbstraction}

@@

where $DT$ is the set of data types (as identified by their names) and $U$ is the set of all possible objects $x$ of all types in $DT$. This means that for each type $T\in DT$, the preimage $\pi^{1}(T)\subset U $ is the domain of $T$, and a value $x \in \pi^{1}(T)\subset U$ is an object of type $T$. Spivak then defines a schema $(C, \sigma)$ of type $\pi$, where $\pi$ is the universe of all types, such that 
\begin{equation}
\sigma: C \rightarrow DT
\end{equation}
where $C$ is a finite set of names of columns in a database or a list of attributes.

@@

>>>>

\begin{figure}[ht]
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
    \label{fig:fiberbundle}
\end{figure}

@@

\begin{figure}[ht]
    \includegraphics[width=0.4\linewidth]{figures/sections/math/k_qspace.png}
    \label{fig:kquote}
\end{figure}

$K$ is the quotient space of $E$, meaning it is the set of equivalence classes of elements $p$ in of $E$ defined via the map $\pi: E \rightarrow K$ that sends each point $p \in E$ to its equivalence class in $[p] \in K$ \cite{QuotientSpaceTopology2020,QuotientSpaceTopology2020}. As shown in figure~\ref{fig:kquote}, the fibers $F$ divide $E$ into smaller spaces consisisting of $F$ and an open set neighborhood around $F$. This subdivision is projected down to the toplology $\tau_k$

@@

\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_1k.png}
    %% add box around neighboring P and Map
    \label{fig:k_data}
\end{figure}
\begin{figure}[ht]
    \includegraphics[width=0.2\linewidth]{figures/sections/math/temp_2k.png}
\end{figure}

We use $K$ to encode the connectivity of the points $p$. In figure~\ref{fig:k_data}, there is only one data field in $p$, temperature, but the points $p$ are connected differently. In a timeseries, the temperature $p$ at time $t$ is dependent on the value at $p_{t-1}$ and $p_{t+1}$ is dependent on the value in $p_t$; this connectivity is expressed as a one dimensional $K$ where $K$ is the number line. In the case of the map, every point $p$ is dependent on its nearest neighbors on the plane, and one way to express this is by encoding $K$ as a plane. $K$ does not know the time or latitude or longitude of the point - those are metadata variables potentially encoded in $p$ because they are ways of describing the connectivity rather than the connectivity itself. The mapping $sigma: K \rightarrow E$ provides the binding between the key on $K$ and the value $p$ in $E$ \cite{munznerChDataAbstraction}.

@@

where $DT$ is the set of data types (as identified by their names) and $U$ is the disjoint set of all possible objects $x$ of all types in $DT$. This means that for each type $T\in DT$, the preimage $\pi^{-1}(T)\subset U $ is the domain of $T$, and $x \in \pi^{1}(T)\subset U$ is an object of type $T$. Spivak then defines a schema $(C, \sigma)$ of type $\pi$, where $\pi$ is the universe of all types, such that 
\begin{equation}
\sigma: C \rightarrow DT
\end{equation}
where $C$ is the finite set of names of data fields in $E$. The set of all values restricted to the datatypes in $DT$

\begin{equation}
    \begin{tikzcd}
            U_{\sigma} \arrow[d, "\pi_{\sigma}" description] \arrow[r] & U \arrow[d, "\pi" description] \\
            C \arrow[r, "\sigma" description]                          & DT                            
    \end{tikzcd}
\end{equation}

@@

The record function is the sigma function
